Macro Impacts

### 2016-08-19 Macro Impacts Revised.tex
Thermal source revisions/v2
Added a variation of the approach presented, with a couple of
corrections.  Interestingly, the results of micrometers to tens of
micrometers remains true.

\section{Revised Estimate}
Suppose we have the displacement field
u &= \int\f{\diff^3 k}{(2\pi)^3}U(\vec k)e^{-\I(\vec k\cdot \vec x-k v_p t)}\,.
Since we want the maximum displacement, we set $t=0$. In the case that $U$ doesn't depend on $\hat k$, we have
u &=\int\f{\diff^3 k}{(2\pi)^3}U(k)e^{-\I(\vec k\cdot \vec x)}\,,\\
&=\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^3}k^2\sin\theta U( k)e^{-\I k r \cos\phi}\,,\\
&=\int\f{\diff k}{(2\pi)^2}k^2U( k) J_0(k r)\,.
When $kr\ll 1$, we have
u&\approx \int\f{\diff k}{(2\pi)^2}k^2U(k)\,.
The requirement that $kr\ll 1$ may determine the maximum size of the pixels. Then
\partial_t u =\I v_p\int\f{\diff^3 k}{(2\pi)^3}kU(\vec k)e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,
\abs{\partial_t u}^2 = v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')e^{-\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}
E = \rho\int\diff^3 x (\partial_t u)^2 &= v_p^2\rho\int\diff^3 x\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')e^{\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho\int\diff^3 xe^{\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho\int\diff^3 xe^{\I((\vec k'-\vec k)\cdot \vec x-(k'-k) v_p t)}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho \delta(\vec k-\vec k')e^{\I(k-k') v_p t}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho \delta(\vec k-\vec k')\,,\\
&=\rho v_p^2\int\f{\diff^3 k}{(2\pi)^3}k^2\abs{U(\vec k)}^2\,.
Assuming $U$ has no $\hat k$ dependence
E&=2\rho v_p^2\int_{0}^{\infty}\f{\diff k}{(2\pi)^2}k^4\abs{U(k)}^2\,.
Define
E_k &=2\rho v_p^2\int_{0}^{k}\f{\diff k'}{(2\pi)^2}k'^4\abs{U(k')}^2\,.
Then
\td{E_k}{k}{} =\f{2\rho v_p^2}{(2\pi)^2}k^4\abs{U(k)}^2
\abs{U(k)} = \f{2\pi}{\sqrt{2\rho v_p^2}}\f{1}{k^2}\sqrt{\td{E_k}{k}{}}\,.
Whence
u \leq \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.
In our case, when we want to only consider modes up to some $k$, we have
u_k \leq \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}
For us, before attenuation we have
E_k = C_1 k^2\,,
so before attenuation we have
\td{E_k'}{k'}{} = 2 C_1 k'\,,
and after attenuation
\td{E_k'}{k'}{} = 2 C_1 k'e^{-k' v_p\f{T}{Q}}\,,
whence, the maximum amplitude in the vicinity of the ray impact is
u &\leq \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
&=\f{\sqrt{E_{\te{ray}}}}{2\pi k\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,.
This equation tells us the maximum displacement within the healpix pixel. Note that this is not a function of the area of the pixel. This is reasonable because the energy distribution is not a function of our partition of the sphere.
\section{Directed Ray}
This time, we assume the oscillation is just in the $x$ direction.
u(\vec x,t) =\int\f{\diff k}{2\pi}\, U(k)\chi_{A_{\te{ray}}} e^{-\I k(x -v_p t)}\,.
The part of $u$ that detectors will pick up is
u(\vec x,t) =\int_0^k\f{\diff k'}{2\pi}\, U(k')\chi_{A_{\te{ray}}} e^{-\I k'(x -v_p t)}\,.
We approximate in the $x$ direction
u(x,t) &\leq \int_0^k\f{\diff k'}{2\pi}\, \abs{U(k')}\,.
Now, we make use of the orthogonality of the basis functions to eliminate the spatial integral as above. Denote the width of the pulse as $L$.
E &=\rho\int\diff^3 x\abs{\partial_t u}^2\,,\\
&=\rho v_p^2\int\diff^3 x\chi_{A_{\te{ray}}}\int\f{\diff k}{2\pi}\int\f{\diff k'}{2\pi}k k'U(k)\bar U(k') e^{-\I (k-k')(x -v_p t)}\,,\\
&=\rho v_p^2 A_{\te{ray}}\int\diff x\int\f{\diff k}{2\pi}\int\f{\diff k'}{2\pi}k k'U(k)\bar U(k') e^{-\I (k-k')(x -v_p t)}\,,\\
&=\rho v_p^2 A_{\te{ray}}\int\f{\diff k}{2\pi}\int \diff k'k k'U(k)\bar U(k') \delta(k-k')e^{\I (k-k')v_p t}\,,\\
&=\rho v_p^2 A_{\te{ray}}\int\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,.
We denote, as before,
E_k = \rho v_p^2 A_{\te{ray}}\int_0^k\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,,
so
\td{E_k}{k}{} =\f{\rho v_p^2 A_{\te{ray}}k^2}{2\pi}\abs{U(k)}^2\,.
\abs{U(k)} = \sqrt{\f{2\pi}{\rho v_p^2 A_{\te{ray}}}}\f{1}{k}\sqrt{\td{E_k}{k}{}}\,,
and so
u(x,t) \leq \sqrt{\f{1}{2\pi \rho v_p^2 A_{\te{ray}}}}\int_0^k\f{\diff k'}{k'}\sqrt{\td{E_k'}{k'}{}}\,.
Hence, in our case, where
\td{E_k}{k}{} = 2C_1 k e^{-C_2 k}\,.
we have
u(x,t) \leq \sqrt{\f{2}{\rho v_p^2 A_{\te{ray}}}}\sqrt{\f{C_1}{C_2}}\te{Erf}\ps{\sqrt{\f12 C_2 k}}
We can write
C_1 = \f{E_\te{ray}}{k^2}\,,
u(x,t) \leq \sqrt{\f{2}{\rho v_p^2 A_{\te{ray}}}}\sqrt{\f{E_\te{ray}}{C_2}}\f1k\te{Erf}\ps{\sqrt{\f12 C_2 k}}\,.
Now, suppose that the time width of the wave is $\Delta T$. This corresponds to the minimum angular frequency associated to the wave. 
\Delta T \geq \f{2\pi}{\omega} = \f{2\pi}{v_p k}\,.
k \geq\f{2\pi}{v_p\Delta T}\,.
\section{Maximum Detectible Surface Area}
\indent

@@

\pagebreak
\section{Thermal Source}
As relayed in an email to Josh, observe that the thermal source is
\begin{align}
T = \f{v_0^2}{c_p}\theta(r_X-r)\,,
\end{align}
where $c_p$ is the specific heat capacity of the material. The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
\begin{align}
\partial_t T - \alpha\nabla^2 T = 0
\end{align}
where $\alpha$ is known as the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
\begin{align}
\partial_t T - \alpha\nabla_r T = 0
\end{align}
We now Fourier transform in $r$ and $\phi$, yielding
\begin{align}
\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
\end{align}
where
\begin{align}
\tilde T = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
\end{align}
Now, we integrate
\begin{align}
\tilde T = C_1e^{-\alpha k_r^2 t}
\end{align}
Now, to determine $C_1$, we set $T = \f{v_0^2}{c_p}\theta(r_X-r)$ at $t = 0$. Observe, this initial condition corresponds to the transformed statement
\begin{align}
\tilde T(0) = \f{r_X}{k_r}J_1(k_r r_X)\,.
\end{align}
This fixes $C_1$. We now inverse transform and obtain
\begin{align}
T &= \int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}\f{r_X}{k_r}J_1(k_r r_X) J_0(k_r r)\,,\\
&=r_X\int_0^\infty \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) J_0(k_r r)\,.
\end{align}
We'll have to do this integral numerically. However, we are interested in solving for $r(t)$ such that $T(r(t),t) = T_{\te{melt}}$. We then want to find $\dot r$. Denote this special $r(t)$ as $r_\te{melt}$. Then
\begin{align}
\f{T_\te{melt}}{r_X} = \int_0^\infty \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) J_0(k_r r_\te{melt})
\end{align}
and
\begin{align}
0&=\int_0^\infty \diff k_r \ps{e^{-\alpha k_r^2 t} J_1(k_r r_X) \p{-k_r\dot r_\te{melt}}J_1(k_r r_\te{melt}) +  \p{-\alpha k_r^2}e^{-\alpha k_r^2 t} J_1(k_r r_X)J_0(k_r r_\te{melt})}\,,\\
0&=\int_0^\infty k_r \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) \ps{\p{\dot r_\te{melt}}J_1(k_r r_\te{melt}) +  \p{\alpha k_r}J_0(k_r r_\te{melt})}\,.
\end{align}
\pagebreak\\
Eh... None of this is producing useful results, i.e. those we can use to solve for $r_\te{melt}$. Let's consider a delta source i.e.
\begin{align}
T = \f{v_0^2}{c_p}r_X\delta(r)\,.
\end{align}
Then
\begin{align}
C_1 =2\pi \f{v_0^2}{c_p}r_x
\end{align}
Thus,
\begin{align}
T &= \int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)2\pi \f{v_0^2}{c_p}r_x\,,\\
&=\f{r_X v_0^2}{2 c_p t \alpha} e^{-\f{r^2}{4t\alpha}}\,.
\end{align}
Setting $T = T_\te{melt}$, we have
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,.
\end{align}
where we've taken the positive branch, since we only care about the melt radius increasing. Then
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{r_Xv_0^2}{2 c_p t\alpha T}} - 1}{\sqrt{\ln\p{\f{r_Xv_0^2}{2 c_p t\alpha T}}}}\,.
\end{align}
For our parameters, it is a good approximation to take
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{r_Xv_0^2}{2 c_p\alpha T}}}\,.
\end{align}
Thus, the time at which the velocity of the melt front is that of the speed of sound is
\begin{align}
t_{\te{fast}} = \f{\alpha}{v_p^2}\ln\p{\f{r_Xv_0^2}{2 c_p\alpha T_\te{melt}}}
\end{align}
at a radius, which is a good approximation in our case, of
\begin{align}
r_\te{fast melt} =  2\f{\alpha}{v_p}\ln\ps{\f{r_X v_0^2}{2 c_p \alpha T_\te{melt}}}
\end{align}
which is on the order of micrometers to tenths of micrometers for our case.
\end{document}

>>>>

\section{Revised Estimate}
Suppose we have the displacement field
\begin{align}
u &= \int\f{\diff^3 k}{(2\pi)^3}U(\vec k)e^{-\I(\vec k\cdot \vec x-k v_p t)}\,.
\end{align}
Since we want the maximum displacement, we set $t=0$. In the case that $U$ doesn't depend on $\hat k$, we have
\begin{align}
u &=\int\f{\diff^3 k}{(2\pi)^3}U(k)e^{-\I(\vec k\cdot \vec x)}\,,\\
&=\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^3}k^2\sin\theta U( k)e^{-\I k r \cos\phi}\,,\\
&=\int\f{\diff k}{(2\pi)^2}k^2U( k) J_0(k r)\,.
\end{align}
When $kr\ll 1$, we have
\begin{align}
u&\approx \int\f{\diff k}{(2\pi)^2}k^2U(k)\,.
\end{align}
The requirement that $kr\ll 1$ may determine the maximum size of the pixels. Then
\begin{align}
\partial_t u =\I v_p\int\f{\diff^3 k}{(2\pi)^3}kU(\vec k)e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,
\end{align}
and
\begin{align}
\abs{\partial_t u}^2 = v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')e^{-\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}
\end{align}
Thus
\begin{align}
E = \rho\int\diff^3 x (\partial_t u)^2 &= v_p^2\rho\int\diff^3 x\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')e^{\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho\int\diff^3 xe^{\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho\int\diff^3 xe^{\I((\vec k'-\vec k)\cdot \vec x-(k'-k) v_p t)}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho \delta(\vec k-\vec k')e^{\I(k-k') v_p t}\,,\\
&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho \delta(\vec k-\vec k')\,,\\
&=\rho v_p^2\int\f{\diff^3 k}{(2\pi)^3}k^2\abs{U(\vec k)}^2\,.
\end{align}
Assuming $U$ has no $\hat k$ dependence
\begin{align}
E&=2\rho v_p^2\int_{0}^{\infty}\f{\diff k}{(2\pi)^2}k^4\abs{U(k)}^2\,.
\end{align}
Define
\begin{align}
E_k &=2\rho v_p^2\int_{0}^{k}\f{\diff k'}{(2\pi)^2}k'^4\abs{U(k')}^2\,.
\end{align}
Then
\begin{align}
\td{E_k}{k}{} =\f{2\rho v_p^2}{(2\pi)^2}k^4\abs{U(k)}^2
\end{align}
Hence
\begin{align}
\abs{U(k)} = \f{2\pi}{\sqrt{2\rho v_p^2}}\f{1}{k^2}\sqrt{\td{E_k}{k}{}}\,.
\end{align}
Whence
\begin{align}
u \leq \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.
\end{align}
In our case, when we want to only consider modes up to some $k$, we have
\begin{align}
u_k \leq \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}
\end{align}
For us, before attenuation we have
\begin{align}
E_k = C_1 k^2\,,
\end{align}
so before attenuation we have
\begin{align}
\td{E_k'}{k'}{} = 2 C_1 k'\,,
\end{align}
and after attenuation
\begin{align}
\td{E_k'}{k'}{} = 2 C_1 k'e^{-k' v_p\f{T}{Q}}\,,
\end{align}
whence, the maximum amplitude in the vicinity of the ray impact is
\begin{align}
u &\leq \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
&=\f{\sqrt{E_{\te{ray}}}}{2\pi k\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,.
\end{align}
This equation tells us the maximum displacement within the healpix pixel. Note that this is not a function of the area of the pixel. This is reasonable because the energy distribution is not a function of our partition of the sphere.
\pagebreak

\section{Directed Ray}
This time, we assume the oscillation is just in the $x$ direction.
\begin{align}
u(\vec x,t) =\int\f{\diff k}{2\pi}\, U(k)\chi_{A_{\te{ray}}} e^{-\I k(x -v_p t)}\,.
\end{align}
The part of $u$ that detectors will pick up is
\begin{align}
u(\vec x,t) =\int_0^k\f{\diff k'}{2\pi}\, U(k')\chi_{A_{\te{ray}}} e^{-\I k'(x -v_p t)}\,.
\end{align}
We approximate in the $x$ direction
\begin{align}
u(x,t) &\leq \int_0^k\f{\diff k'}{2\pi}\, \abs{U(k')}\,.
\end{align}
Now, we make use of the orthogonality of the basis functions to eliminate the spatial integral as above. Denote the width of the pulse as $L$.
\begin{align}
E &=\rho\int\diff^3 x\abs{\partial_t u}^2\,,\\
&=\rho v_p^2\int\diff^3 x\chi_{A_{\te{ray}}}\int\f{\diff k}{2\pi}\int\f{\diff k'}{2\pi}k k'U(k)\bar U(k') e^{-\I (k-k')(x -v_p t)}\,,\\
&=\rho v_p^2 A_{\te{ray}}\int\diff x\int\f{\diff k}{2\pi}\int\f{\diff k'}{2\pi}k k'U(k)\bar U(k') e^{-\I (k-k')(x -v_p t)}\,,\\
&=\rho v_p^2 A_{\te{ray}}\int\f{\diff k}{2\pi}\int \diff k'k k'U(k)\bar U(k') \delta(k-k')e^{\I (k-k')v_p t}\,,\\
&=\rho v_p^2 A_{\te{ray}}\int\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,.
\end{align}
We denote, as before,
\begin{align}
E_k = \rho v_p^2 A_{\te{ray}}\int_0^k\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,,
\end{align}
so
\begin{align}
\td{E_k}{k}{} =\f{\rho v_p^2 A_{\te{ray}}k^2}{2\pi}\abs{U(k)}^2\,.
\end{align}
Thus
\begin{align}
\abs{U(k)} = \sqrt{\f{2\pi}{\rho v_p^2 A_{\te{ray}}}}\f{1}{k}\sqrt{\td{E_k}{k}{}}\,,
\end{align}
and so
\begin{align}
u(x,t) \leq \sqrt{\f{1}{2\pi \rho v_p^2 A_{\te{ray}}}}\int_0^k\f{\diff k'}{k'}\sqrt{\td{E_k'}{k'}{}}\,.
\end{align}
Hence, in our case, where
\begin{align}
\td{E_k}{k}{} = 2C_1 k e^{-C_2 k}\,.
\end{align}
we have
\begin{align}
u(x,t) \leq \sqrt{\f{2}{\rho v_p^2 A_{\te{ray}}}}\sqrt{\f{C_1}{C_2}}\te{Erf}\ps{\sqrt{\f12 C_2 k}}
\end{align}
We can write
\begin{align}
C_1 = \f{E_\te{ray}}{k^2}\,,
\end{align}
hence
\begin{align}
u(x,t) \leq \sqrt{\f{2}{\rho v_p^2 A_{\te{ray}}}}\sqrt{\f{E_\te{ray}}{C_2}}\f1k\te{Erf}\ps{\sqrt{\f12 C_2 k}}\,.
\end{align}
Now, suppose that the time width of the wave is $\Delta T$. This corresponds to the minimum angular frequency associated to the wave. 
\begin{align}
\Delta T \geq \f{2\pi}{\omega} = \f{2\pi}{v_p k}\,.
\end{align}
Thus
\begin{align}
k \geq\f{2\pi}{v_p\Delta T}\,.
\end{align}
\pagebreak
\section{Maximum Detectible Surface Area}
\indent

@@

\pagebreak
\section{Thermal Source}
As relayed in an email to Josh, observe that the thermal source is
\begin{align}
T = \f{v_0^2}{c_p}\theta(r_X-r)\,,
\end{align}
where $c_p$ is the specific heat capacity of the material. The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
\begin{align}
\partial_t T - \alpha\nabla^2 T = 0
\end{align}
where $\alpha$ is known as the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
\begin{align}
\partial_t T - \alpha\nabla_r T = 0
\end{align}
We now Fourier transform in $r$ and $\phi$, yielding
\begin{align}
\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
\end{align}
where
\begin{align}
\tilde T = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
\end{align}
Now, we integrate
\begin{align}
\tilde T = C_1e^{-\alpha k_r^2 t}
\end{align}
Now, to determine $C_1$, we set $T = \f{v_0^2}{c_p}\theta(r_X-r)$ at $t = 0$. Observe, this initial condition corresponds to the transformed statement
\begin{align}
\tilde T(0) = \f{r_X}{k_r}J_1(k_r r_X)\,.
\end{align}
This fixes $C_1$. We now inverse transform and obtain
\begin{align}
T &= \int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}\f{r_X}{k_r}J_1(k_r r_X) J_0(k_r r)\,,\\
&=r_X\int_0^\infty \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) J_0(k_r r)\,.
\end{align}
We'll have to do this integral numerically. However, we are interested in solving for $r(t)$ such that $T(r(t),t) = T_{\te{melt}}$. We then want to find $\dot r$. Denote this special $r(t)$ as $r_\te{melt}$. Then
\begin{align}
\f{T_\te{melt}}{r_X} = \int_0^\infty \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) J_0(k_r r_\te{melt})
\end{align}
and
\begin{align}
0&=\int_0^\infty \diff k_r \ps{e^{-\alpha k_r^2 t} J_1(k_r r_X) \p{-k_r\dot r_\te{melt}}J_1(k_r r_\te{melt}) +  \p{-\alpha k_r^2}e^{-\alpha k_r^2 t} J_1(k_r r_X)J_0(k_r r_\te{melt})}\,,\\
0&=\int_0^\infty k_r \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) \ps{\p{\dot r_\te{melt}}J_1(k_r r_\te{melt}) +  \p{\alpha k_r}J_0(k_r r_\te{melt})}\,.
\end{align}
\pagebreak\\
Eh... None of this is producing useful results, i.e. those we can use to solve for $r_\te{melt}$. Let's consider a delta source i.e.
\begin{align}
T = \f{v_0^2}{c_p}r_X\delta(r)\,.
\end{align}
Then
\begin{align}
C_1 =2\pi \f{v_0^2}{c_p}r_x
\end{align}
Thus,
\begin{align}
T &= \int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)2\pi \f{v_0^2}{c_p}r_x\,,\\
&=\f{r_X v_0^2}{2 c_p t \alpha} e^{-\f{r^2}{4t\alpha}}\,.
\end{align}
(David, what happened to the factor of $2\pi$?)
Setting $T = T_\te{melt}$, we have
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,.
\end{align}
where we've taken the positive branch, since we only care about the melt radius increasing. Then
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{r_Xv_0^2}{2 c_p t\alpha T}} - 1}{\sqrt{\ln\p{\f{r_Xv_0^2}{2 c_p t\alpha T}}}}\,.
\end{align}
For our parameters,  it is a good approximation to take
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{r_Xv_0^2}{2 t c_p\alpha T}}}\,.
\end{align}
Thus, the time at which the velocity of the melt front is that of the speed of sound is
\begin{align}
t_{\te{fast}} = \f{\alpha}{v_p^2}\ln\p{\f{r_Xv_0^2}{2 c_p\alpha T_\te{melt}}}
\end{align}
at a radius, which is a good approximation in our case, of
\begin{align}
r_\te{fast melt} =  2\f{\alpha}{v_p}\ln\ps{\f{r_X v_0^2}{2 c_p \alpha T_\te{melt}}}
\end{align}
which is on the order of micrometers to tenths of micrometers for our case.

\pagebreak
Note: The following is based on the above written by David, and modified by Josh (David, feel free to take whatever you'd like and apply to the above):

The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
\begin{align}
\partial_t T - \alpha\nabla^2 T = 0
\end{align}
where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
\begin{align}
\partial_t T - \alpha\nabla_r T = 0
\end{align}
We now Fourier transform in $r$ and $\phi$, yielding
\begin{align}
\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
\end{align}
where
\begin{align}
\tilde T =  \int_0^\infty r \diff r\int_{0}^{2\pi} T e^{i r(k_x\cos\phi +k_y\sin\phi)}\diff \phi\, = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
\end{align}
where
\begin{align}
k_r = k_x\cos\phi +k_y\sin\phi
\end{align}
Now, we integrate $\partial_t\tilde T =-\alpha k_r^2 \tilde T\,$ and find that
\begin{align}
\tilde T = C_1e^{-\alpha k_r^2 t}.
\end{align}

Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\delta(r),
\end{align}
Then, taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
\begin{align}
C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{2\pi i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
\end{align}
where the factor of $2 \pi$ comes from the $\phi$ integral.
$T$ in real space is given by inverting the Fourier transform:
\begin{align}
T(r,t) &= \int_0^\infty k_r \diff{k_r}\tilde{T} = 4\pi^2\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
&=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
\end{align}
(I'm not sure about the last equality given that I'm still a bit unclear about the factors of $2\pi$ for the inverse transform as noted above after eq. (300) It would seem there are factors from $C_1$ and $\tilde{T}$.  However, the rest of what follows holds, up to some factors of $2\pi$ that hopefully we can clarify).
Setting $T = T_\te{melt}$, we have
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
\end{align}
where we've taken the positive branch of the square root, since we only care about the melt radius increasing. Then taking the derivative w.r.t to time gives
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}}\,.
\end{align}
Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a good approximation to take
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
\end{align}
Thus, the time at which the velocity of the melt front is that of the speed of sound is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
\begin{align}
t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
\end{align}
Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a good approximation in our case, gives
\begin{align}
r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
}}}\,.
\end{align}
Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$ which is true for the parameters at hand.  Thus, we have,
\begin{align}
r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}.
\end{align}
which is on the order of micrometers to tenths of micrometers for our case.

\end{document}
